S\&DS 431 Final Project Proposal

### 2024-11-24 proposal.tex
Begin writing

\author{%
  Calder K. Katyal\\
  Undergraduate\\
  Yale University\\
  New Haven, CT 06511 \\
  \texttt{calder.katyal.edu} \\
}

@@

@@

>>>>

\author{%
  Calder K. Katyal; Sebastien Lowy\\
  Undergraduates\\
  Yale University\\
  New Haven, CT 06511 \\
  \texttt{calder.katyal.edu; sebastien.lowy@yale.edu} \\
}

@@

In this research project we propose a novel method to significantly reduce the computational cost of performing Djikstra's Shortest Path Algorithm in temporal graph data with dynamically evolving edge weights. In particular, we employ a Graph Neural Network (GNN) to predict edge importance scores and prune the graph at each timestep, significantly reducing the search space of Djikstra's algorithm. By incorporating node and edge level features as well as structural information into our model at each timestep, we can optimize Djikstra to real-world scenarios where graphs exhibit structured evolution.

@@

Possibility: https://www.microsoft.com/en-us/research/publication/t-drive-trajectory-data-sample/
